\section{The Cairngorms}

These are ordered clockwise, from the South-East.

\subsection{South-east Cairngorms}

\begin{munros}
\item Mayar and Driesh. \tick

\item Mount Keen.  Alternatively from Glen Tanar. 
\end{munros}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{East of Braemar}

\begin{munros}
\item \target Ben Avon.  33.5km, 1004m; 8--10 hrs.  NO188912.  Could be combined
  with Beinn a' Bhùird.  \tick

\item \target White Mounth Munros: Lochnagar, Càrn a' Choire Bhòidheach, Càrn an
  t-Sagairt Mòr, Cairn Bannoch, and Broad Cairn.  \tick

\item Mount Keen.  29km, 1228m; 9--11 hrs.  NO309851.  Alternatively from
  south.  \tick
\end{munros}


%%%%%

\subsection{West of Braemar}

\begin{munros}
\item Beinn Iutharn Mhòr and Càrn Bhac.

\item An Sgarsoch and Càrn an Fhidhleir.

\item Càrn a' Mhàim.

\item\target Beinn Mheadhoin and Derry Cairngorm.  31km, 1200m; 9--10~hrs.
  NO062898.  Or from Ski Centre.  \tick

\item Beinn a' Chaorainn and Beinn Bhreac.


\item \target Beinn a' Bhùird.  28km, 959m; 7--9 hrs.  NO116909.  Could be
  combined with Ben Avon.  \tick
\end{munros}
%%%%%%%%%%

\subsection{A93}

\begin{munros}
\item Glas Tulaichean and Càrn an Rìgh

\item
Glas Maol Munros: Càrn an Tuirc, Cairn of Claise, Glas Maol, and Creag Leacac.

\item The Cairnwell Munros: Càrn Aosda, Càrn a' Ghèoidh, and The Cairnwell.

\item An Socach.

\item Tolmount and Tom Buidhe.
\end{munros}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Blair Atholl}

\begin{munros}
\item Beinn a' Ghlò: Càrn Liath, Braigh Coire Chruinn-bhalgain, and Càrn nan
  Gabhar.

\item Càrn a' Chlamain.

\item Beinn Dearg. \tick
\end{munros}

%%%%%

\subsection{Pass of Drumochter}

\begin{munros}
\item
Beinn Udlamain and Sgàirneach Mhòr.  Could be combined with following.  \tick

\item
A' Mharconaich and Geal Chàrn.   11.5km, 731m; 4--6~hrs.  NN627791. \tick

\item Càrn na Caim and A' Bhuidheanach Bheag. \tick
\end{munros}

%%%%%

\subsection{Dalwhinnie}

\begin{munros}
\item \target Ben Alder and Beinn Bheòil, from Culra.  17km, 1021m;
  7--8~hrs. NN522761. \tick

\item \target Càrn Dearg, Geal Chàrn, Aonach Beag and Beinn Èibhinn from
  Culra.  18.5km, 1110m; 8--9 hrs.  NN522761.  \tick

\item
Meall Chuaich.  \tick
\end{munros}

%%%%%

\subsection{Glen Feshie}

\begin{munros}
\item Sgòr Gaoith.  \tick

\item \target Beinn Bhrotain and Monadh Mòr.  29km, 1505m; 9--11 hrs.
  NN850985.  \tick

\item Mullach Clach a' Bhlàir.
\end{munros}

%%%%%

\subsection{Glen More and the Ski Centre}

\begin{munros}
\item Bynack More.

\item\target The Devil's Point, Cairn Toul, Sgòr an Lochain Uaine, Braeriach.
  36km, 1820m; 13 hrs.  NH984073.  \tick

\item\target Ben Macdui and Cairngorm.  17.5km, 932m; 6--8~hrs.  NH989059.
  Could combine with following.  \tick

\item\target Beinn Mheadhoin and Derry Cairngorm.  Approx.\ 24km, 2000m;
  10-12~hrs. NH989059.  Or from Lin of Dee.  \tick
\end{munros}


%%%%%
