\section{Glen Shiel}

Including surrounding areas.  From East to West.

\subsection{Glen Shiel}

\begin{munros}
\item
Càrn Ghluasaid, Sgùrr nan Conbhairean and Sàil Chaorainn.  17.5km, 1260m; 7--8
hrs.  NH144103.  \tick

\item
A' Chralaig and Mullach Fraoch-choire.  13km, 1150m; 6--8 hrs.  NH092121.
Boggy return. \tick

\item
Ciste Dhubh and Am Bathach.  12.5km, 1040m; 5--7 hrs. NH087122.  \tick

\item
\target  South Glen Shiel Ridge: Creag a' Mhaim, Druim Shionnach, Aonach Air
Chrith, Maol Chinn-dearg, Sgùrr an Doire Leathain, Sgùrr an Lochain, Creag nan
Dàmh.  26.75km, 1818m; 9--11~hrs (plus cycle).  NH079117.  \tick

\item
\target Brothers Ridge: Sàileag, Sgùrr a Bhealaich Dheirg, Aonach Meadhoin.
10km, 1274m; 6--8 hrs (plus cycle).  NH009135.  Could be combined with
following.  \tick.

\item
\target Five Sisters of Kintail: Sgùrr na Ciste Duibhe, Sgùrr na Càrnach,
Sgùrr Fhuaran.  15km, 1385m; 8--10 hrs (plus cycle).  NH009135.  \tick

\item \target The Saddle, Forcan Ridge and Sgùrr na Sgìne.  13km;
  1350m; 7--9 hours.  NG965146.  \tick

\item\target\target Sgùrr a' Bhac Chaolais and Buidhe Bheinn (joint Corbett).
  NG965146 (Malagan). 
\end{munros}


\subsection{From Shiel Bridge}

\begin{munros}
\item\target\target Gleanne Undalaine circuit: Sgùrr Mhic Bharraich (Corbett)
  and The Saddle.

\item\target\target Beinn na h-Eaglaise and Beinn nan Caorach (Corbetts).

\item Beinn Sgritheall.  \tick
\end{munros}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Arnisdale}

\begin{munros}
\item
Beinn Sgritheall.  Also possible from Shiel Bridge.  \tick
\end{munros}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Morvich}

\begin{munros}
\item
\target Beinn Fhada.  16.75km; 1234m; 6--7 hours.  NG961211.  Could be
combined with following.  \tick

\item \target A' Ghlas Bheinn.  21km; 1196m; 7--9 hours.  NG961211. \tick
\end{munros}
