
\section{Glen Coe and Fort William}

\subsection{Glen Coe}

From East to West. 

\begin{munros}
\item
Creise and Meall a'Bhùiridh

\item\tick
Buachaille Etive Mòr: Stob Dearg and Stob na Bròige.  13km, 1110m; 7-9
hrs.  NN221563. 

\item\tick
Buachaille Etive Beag: Stob Coire Raineach and Stob Dubh.  8km, 900m; 5--6
hrs.  NN187562.

\item
Bidean nam Bian and Stob Coire Sgreamhach

\item
Aonach Eagach: Meall Dearg and Sgòrr nam Fiannaidh

\item
Sgòr na h-Ulaidh and Meall Lighiche

\item
Beinn a' Bheithir: Sgòrr Dhearg and Sgòrr Dhònuill
\end{munros}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Glen Etive}

\begin{munros}
\item\tick
Stob Coir'an Albannaich and Meall nan Eun

\item\tick
Ben Starav and Glas Bheinn Mhòr

\item\tick
Beinn nan Aighenan.  Can combine with previous. 
\end{munros}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Kinlochleven}

\begin{munros}
\item\tick
Binnein Mòr and Na Gruagaichean.  14km, 1336m; 7--9 hrs.  NN187622.

\item\tick
Sgùrr Èilde Mòr and Binnein Beag.  20km, 1582m; 9--11 hrs.  NN188623.
\end{munros}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Glen Nevis}

From West to East. 

\begin{munros}
\item\target\tick
Stob Ban  and Mullach nan Coirean.  13km, 1155m; 6--8 hrs. NN145683. 

\item\target\tick
The Ring of Steall: An Gearanach, Stob Coire a' Chàirn, Am Bodach and Sgùrr
a'Mhaim.  16km, 1676m; 9--12 hrs.  NN168691.

\item
Aonach Beag and Aonach Mòr
\end{munros}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\subsection{Ben Nevis Range, from North}

From West to East.  As far as Roy Bridge. 

\begin{munros}
\item\tick
Ben Nevis and Càrn Mòr Dearg.  17.5km, 1506m; 10--11hrs.  NN144763.

\item\target\tick
The Grey Corries: Stob Choire Claurigh, Stob Coire an Laoigh and Sgùrr
Chòinnich Mòr. 

\item
Stob Bàn.  Could be combined with previous. 
\end{munros}
